Appendix S1: Supporting Tables and Figures

### 2022-04-28 ms/SI.Rmd
Fix richness of endemic Japanese ferns data
- previously included richness of all ferns

```{r endemism-restricted, fig.width = 5, fig.height = 5}
ggplot() +
  geom_sf(data = japan, fill = "white", color = "transparent", lwd = coast_lwd) +
  geom_sf(data = biodiv_ferns_endemic_spatial, aes(fill = endem_type), color = "transparent") +
  geom_sf(data = japan, fill = "transparent", color = coast_col, lwd = coast_lwd) +
  scale_fill_manual(
    values = canape_cols,
    name = "Endemism type") +
  annotation_scale(location = "tl", width_hint = 0.2) +
  map_theme()
```

@@

Phylogenetic endemism of the ferns of Japan measured using CANAPE (categorical analysis of neo- and paleoendemism), restricted data set including only taxa endemic to Japan.
neo, neodendemic areas (those with an overabundance of short branches); paleo, paleoendemic areas (those with an overabundance of long branches); mixed, significantly endemic sites that have neither an overabundance of short nor long branches; super, highly significantly endemic sites that have neither an overabundance of short nor long branches.
Grid cells without significant endemism in light grey.
Grid cells without at least two taxa endemic to Japan in dark grey.

>>>>

```{r endemism-restricted, fig.width = 5, fig.height = 5}
# Drop one grid cell with NA for endem type
biodiv_ferns_endemic_spatial_no_na <- biodiv_ferns_endemic_spatial %>%
  filter(!is.na(endem_type))

ggplot() +
  geom_sf(data = japan, fill = "white", color = "transparent", lwd = coast_lwd) + #nolint
  geom_sf(data = biodiv_ferns_endemic_spatial_no_na, aes(fill = endem_type), color = "transparent") + #nolint
  geom_sf(data = japan, fill = "transparent", color = coast_col, lwd = coast_lwd) + #nolint
  scale_fill_manual(
    values = canape_cols,
    breaks = names(canape_cols)[names(canape_cols) != "not significant"],
    name = "Endemism type") +
  annotation_scale(location = "br", width_hint = 0.2) +
  map_theme()
```

@@

Phylogenetic endemism of the ferns of Japan measured using CANAPE (categorical analysis of neo- and paleoendemism), restricted data set including only taxa endemic to Japan.
neo, neodendemic areas (those with an overabundance of short branches); paleo, paleoendemic areas (those with an overabundance of long branches); mixed, significantly endemic sites that have neither an overabundance of short nor long branches; super, highly significantly endemic sites that have neither an overabundance of short nor long branches.
Grid cells without significant endemism in light grey.
